Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling

### 2020-03-05 response_to_review_SOLA-D-20-00015_v1.txt

Medium concerns
-----------------------------------------------------------------------------------------
1. All of the multi-panel figures that show longitude-latitude maps (e.g. figure 1, 2, 3 etc) are too small, it is very difficult to see any details. There is a lot of white space between the panels that can be removed, and this would be one way to instantly make the maps larger.

We fully  agree. We improved the use of space in Figures 1 through 3. We also changed colors in the latter (see also query #2 below).

-----------------------------------------------------------------------------------------
2. Figure 3 and 11, bottom panels. I find it difficult to distinguish between the red and magenta colours. Can you replace magenta with a different colour, maybe green?

We fully agree. Actually this affects all following Figures #: 3, 4, 11, and 14. In those, we applied the following changes: Red->Orange and Magenta->Red. These emulate our previous choice of colors in Nuevo et al. (2013) and Lloveras et al. (2017). We like to keep all "up" structures in a "warm" palette. We edited text accordingly all along the manuscript. We believe the colors are now clearly distinguishable in all figures.

@@

-----------------------------------------------------------------------------------------
3. Page 14, paragraph starting at line 34. You discuss the latitudinal distribution of short and long loops, and state that the small legs mainly populate the equatorial latitudes, and longer legs at higher latitudes. But this is a skewed result - their spatial positioning was a criteria for their categorisation, so this should not be presented as a scientific result.

Thanks for pointing this out.... ESTO REQUIERE CAMBIOS EN EL PAPER JUSTIFICANDO CON CLARIDAD LA ELECCION DE LOS LIMITES LATITUDINALES Y LA SELECCION DE SOLO UP EN TYPE II Y III. Y UNA RESPUESTA ACORDE.

@@

PROPONEMOS DEJAR LOS HISTOGRAMAS DE LAS FIGS 12 Y 13 COMO ESTÁN, PERO EXPANDIR LA TABLA 2 A QUE INCLUYA DOS COLUMNAS MÁS INDICANDO ESTOS DOS INDICADORES DE CADA CAMPO "Xi":
* Med(Xi)  (debería aproximarse a los porcentuales y signos entre paréntesis que actualmente informa la Tabla 2).
* MAD = Med(Abs(Xi-Med(Xi))).

LUEGO EDITAMOS TABLA Y TEXTO DEL PAPER.

-----------------------------------------------------------------------------------------
5. You discuss the less reliable results from AIA in coronal holes. The very recent paper by Saqri et al (Solar Physics 295, 2020) is relevant here, and should be referenced.

ESTO FUE SOLUCIONADO. EL ORIGEN DEL PROBLEMA NO RADICA EN STRAY-LIGHT DECON. EL EFECTO DE ESTO EN TOM, APLICADO A DATOS EUVI, FUE EXPLORADO EN LLOVERAS ET AL. (2017). CIERTAMENTE NOS INTERESA INCORPORAR ESTO AL PIPELINE DE AIA SI LA PFS ESTÁ BIEN CARACTERIZADA, PERO ES UN TEMA QUE DEBEMOS INVESTIGAR. EXPLICAR COMO SE SOLUCIONÓ Y REMOVER TODO LO NO NECESARIO EN EL PAPER (AZUL) Y AGREGAR COSAS NUEVAS (ROJO).

@@

-----------------------------------------------------------------------------------------
6. The abstract can be shortened somewhat, reducing the number of introductory sentences and with a little less emphasis on the method and future improvements, and more on the science results. In particular: the results of the energy balance analysis and the estimate of energy flux at the coronal base, which are important.

(TOTALMENTE, HAGAMOS ESTO LUEGO DE EDITAR TODO).

-----------------------------------------------------------------------------------------
7. Page 5, paragraph beginning line 34. You briefly describe fitting the DEM to a Gaussian. I know this approach is covered in detail in Nuevo 2015, but I would like a little more detail here. You should mention that, in general, DEMs do not necessarily have a clean Gaussian profile and that more complicated inversions are needed (reference https://ui.adsabs.harvard.edu/abs/2012A%26A...539A.146H/abstract , https://ui.adsabs.harvard.edu/abs/2019SoPh..294..135M/abstract , https://ui.adsabs.harvard.edu/abs/2019SoPh..294..136P/abstract ). Then explain briefly why DEMT leads to cleaner, non-multithermal profiles (due to the 3D spatial reconstruction of the line of sight). I assume that this is why you can use a straightforward Gaussian fit? Also efficiency?

Thanks for this comment and the references. As the LDEM describes the temperature distribution of the plasma in a specific voxel it does not deal with different large scale structures, as it usually it may be the case for the DEM describing the plasma alog a full line-of.sight (LOS). In that sense one can expect as you say, cleaner, profiles than those observed by DEM studies. Still, if one adds tbhe 335 A channel, which adds two sensitivity poits at ~ 1.0 MK and ~ 2.5 MK, one finds that a a bi-Gaussian LDEM model best predics all the tomographic emissivities. That is the main conclusion of Nuevo et. al. (2015). The interpretation in that case is that the unresolved independent strands threading the voxel can have two different characteristic temperatures. Nuevo et al. (2015). So in this sense, the plasma within the voxel can be multi-thermal. As for efficiency, the parametric technique is comparably efficient independently of the chosen model. We did read the  We expanded this discussion in the text.

### 2020-03-05 lloveras_2020_v2.tex
tablas con numeros acomodados en type III
lloveras_2020_v2.tex ahora tiene los nombres de las figuras correctas y ademas se mejorarons estilos de varias figuras

\usepackage[hyperref,optionalrh,solaromanenum]{spr-sola-addons} % For Solar Physics 
%\usepackage{epsfig}                     % For eps figures, old commands
\usepackage{graphicx}                    % For eps figures, newer & more powerfull
%\usepackage{courier}                    % Change the \texttt command to courier style
\usepackage{amssymb}                     % useful mathematical symbols
\usepackage{color}                       % For color text: \color command
\usepackage{breakurl}                    % For breaking URLs easily trough lines
\def\UrlFont{\sf}                        % define the fonts for the URLs
\usepackage{comment}
\usepackage{setspace}
\usepackage[utf8]{inputenc}

%% Local definitions
%% please place your own definitions here and don't use \def but
%% \newcommand{}{} or 
%% \renewcommand{}{} if it is already defined in LaTeX
\renewcommand{\deg}{$^\circ$}
\newcommand{\mdeg}{^\circ}
\newcommand{\rsun}{R{$_\odot$}}
\renewcommand{\l}{\lambda_{\rm N}}%\lambda_
\newcommand{\mrsun}{{\rm R_\odot}}
\newcommand{\med}{{\rm Md}}
\newcommand{\avgTe}{\left<\Tm\right>}
\newcommand{\MK}{{\rm MK}}
\newcommand{\cm}{{\rm cm}}
\newcommand{\cminvc}{\cm^{-3}}
\newcommand{\cminvs}{\cm^{-2}}
\newcommand{\erg}{{\rm erg}}
\newcommand{\s}{{\rm s}}
\newcommand{\sdev}{{\rm SD}}
\newcommand{\mean}{{\rm Mn}}
\newcommand{\deltat}{$\delta$}
\newcommand{\LDEM}{{\rm LDEM}}
\newcommand{\FBE}{{\rm FBE}}
\newcommand{\TRF}{{\rm TRF}}
\newcommand{\lN}{\lambda_N}
\newcommand{\NCB}{N_{\rm CB}}
\newcommand{\Nqi}{N_{\rm QI}}
\newcommand{\dr}{\triangledown_r}
\newcommand{\er}{\mathbf{e}_r}
\newcommand{\Te}{T_{\rm e}}
\newcommand{\Tm}{T_{\rm m}}
\newcommand{\aTm}{\left<\Tm\right>}
\newcommand{\Tmi}{T_{{\rm m},i}}
\newcommand{\Ne}{N_{\rm e}}
\newcommand{\Nm}{N_{\rm m}}
\newcommand{\Nsqmi}{N^2_{{\rm m},i}}
\newcommand{\Nsqm}{N^2_{{\rm m}}}
\newcommand{\rhoTr}{\rho(T,r)}
\newcommand{\Tefit}{T_{e,{\rm fit}}}
\newcommand{\sqravgNi}{\sqrt{\Nsqmi}}
\newcommand{\sqravgN}{\sqrt{\Nsqm}}
\newcommand{\Tc}{T_{\rm c}}
\newcommand{\BibTeX}{\textsc{Bib}\TeX}
\newcommand{\etal}{{\it et al.}}
\newcommand{\Pl}{\texttt{+}}
\newcommand{\Mi}{\texttt{-}}

@@

%---------REMOVE THESE OPTIONS AND DEFs BEFORE SUMBISSION---------------------------------------
\usepackage[usenames,dvipsnames]{xcolor} % Las opciones: [USENAMES,DVIPSNAMES] 
                                         % ponen a disposición los colores ejemplificados aquí:
                                         % https://en.wikibooks.org/wiki/LaTeX/Colors
\def\note#1{\textcolor{blue}{NOTE: #1}}
\def\diego#1{\textcolor{red}{#1}}
\def\albert#1{\textcolor{orange}{#1}}
\def\fede#1{\textcolor{ForestGreen}{#1}}
\def\temp#1{\textcolor{gray}{#1}}
%-----------------------------------------------------------------------------------------------

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/Grispoint_2082_demt_paper_test_Rpoint-map.pdf}
\includegraphics[width=0.495\textwidth,clip=]{figs/Grispoint_2208_demt_paper_test_Rpoint-map.pdf}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_full_Rpoint-map.pdf}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_awsom_paper_Rpoint-map.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_full_Rpoint-map.pdf}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_awsom_paper_Rpoint-map.eps}
\caption{\emph{Top panels:} {latitude-longitude location at heliocentric height $r=1.105\,\mrsun$ of all open (grey color) and closed (black color) traced field line legs for which criterion (i) of Section \ref{trace} is met, for both CR-2082 (left) and CR-2208 (right). \emph{Bottom panels}: latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met. {The location of} type 0, I, II and III legs {is shown} in blue, red, {magenta and cyan} color, respectively.}}
\label{rpoint_demt}
\end{center}
\end{figure}

@@

\begin{table}[h!]
\begin{tabular}{l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r  r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r }
\hline
Type    & \multicolumn{4}{c}{$\med(\NCB)$}             & \multicolumn{4}{c}{$\med(\lN)$} & \multicolumn{4}{c}{$\med(\avgTe)$} \\
        & \multicolumn{4}{c}{$[10^8\,{\rm cm}^{-3}]$}  & \multicolumn{4}{c}{$[{\rm 10}^{-2}\,\mrsun]$} & \multicolumn{4}{c}{$[\MK]$} \\
\hline
0    & 1&24 &(\Mi&19\%)  &   7&1 &(\Pl&~3\%) &   1&09 &(\Pl&24\%) \\
I    & 1&15 &(\Mi&10\%)  &   7&5 &(\Pl&29\%) &   1&25 &(\Pl&24\%) \\
II   & 0&98 &(\Mi&20\%)  &   9&9 &(\Pl&19\%) &   1&36 &(\Pl&16\%) \\
III  & 0&66 &(\Mi&12\%)  &   7&7 &(\Pl&15\%) &   0&97 &(\Pl&18\%) \\
\hline          
\end{tabular}
\caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of legs defined in Section \ref{trace}. For CR-2082 values are expressed in absolute terms, while for CR-2208 they are informed as a percentual variation relative to the CR-2082 value.}
\label{tabla_demt}
\end{table}

@@

\begin{table}
\begin{tabular}{l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r  r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r }
\hline
Type    & \multicolumn{4}{c}{$\med(\NCB)$}             & \multicolumn{4}{c}{$\med(\lN)$} & \multicolumn{4}{c}{$\med(\avgTe)$} \\
        & \multicolumn{4}{c}{$[10^8\,{\rm cm}^{-3}]$}  & \multicolumn{4}{c}{$[{\rm 10}^{-2}\,\mrsun]$} & \multicolumn{4}{c}{$[\MK]$} \\
\hline
CR-2082\\
I    & 1&15 &(\Mi&14\%)  &   7&5 &(\Pl&~8\%) &   1&25 &(\Mi&10\%) \\
II   & 0&99 &(\Mi&25\%)  &   9&9 &(\Mi&~2\%) &   1&36 &(\Mi&~2\%) \\
III  & 0&66 &(\Mi&17\%)  &   7&0 &(\Mi&~9\%) &   0&97 &(\Mi&~9\%) \\
\hline          
CR-2208\\
I    & 1&03 &(\Pl&~6\%)  &   9&7 &(\Mi&~8\%) &   1&55 &(\Mi&17\%) \\
II   & 0&79 &(\Pl&~9\%)  &  11&8 &(\Mi&14\%) &   1&58 &(\Mi&~8\%) \\
III  & 0&58 &(\Mi&~3\%)  &   8&9 &(\Mi&18\%) &   1&14 &(\Mi&18\%) \\
\hline   
\end{tabular}
\caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of leg defined in Section \ref{trace}. DEMT values are expressed in absolute terms, while AWSoM results are expressed relative to the corresponding DEMT value.}
\label{tabla_comp}
\end{table}

>>>>

\usepackage[hyperref,optionalrh,solaromanenum]{spr-sola-addons} % For Solar Physics 
%\usepackage{epsfig}                     % For eps figures, old commands
\usepackage{graphicx}                    % For eps figures, newer & more powerfull
%\usepackage{courier}                    % Change the \texttt command to courier style
\usepackage{amssymb}                     % useful mathematical symbols
\usepackage{color}                       % For color text: \color command
\usepackage{breakurl}                    % For breaking URLs easily trough lines
\def\UrlFont{\sf}                        % define the fonts for the URLs
\usepackage{comment}
\usepackage{setspace}
\usepackage[utf8]{inputenc}
\usepackage[usenames,dvipsnames]{xcolor}

%% Local definitions
%% please place your own definitions here and don't use \def but
%% \newcommand{}{} or 
%% \renewcommand{}{} if it is already defined in LaTeX

\def\edit#1{\textcolor{Red}{#1}}
\def\del#1{\textcolor{Blue}{#1}}

\renewcommand{\deg}{$^\circ$}
\newcommand{\mdeg}{^\circ}
\newcommand{\rsun}{R{$_\odot$}}
\renewcommand{\l}{\lambda_{\rm N}}%\lambda_
\newcommand{\mrsun}{{\rm R_\odot}}
\newcommand{\med}{{\rm Md}}
\newcommand{\avgTe}{\left<\Tm\right>}
\newcommand{\MK}{{\rm MK}}
\newcommand{\cm}{{\rm cm}}
\newcommand{\cminvc}{\cm^{-3}}
\newcommand{\cminvs}{\cm^{-2}}
\newcommand{\erg}{{\rm erg}}
\newcommand{\s}{{\rm s}}
\newcommand{\sdev}{{\rm SD}}
\newcommand{\mean}{{\rm Mn}}
\newcommand{\deltat}{$\delta$}
\newcommand{\LDEM}{{\rm LDEM}}
\newcommand{\FBE}{{\rm FBE}}
\newcommand{\TRF}{{\rm TRF}}
\newcommand{\lN}{\lambda_N}
\newcommand{\NCB}{N_{\rm CB}}
\newcommand{\Nqi}{N_{\rm QI}}
\newcommand{\dr}{\triangledown_r}
\newcommand{\er}{\mathbf{e}_r}
\newcommand{\Te}{T_{\rm e}}
\newcommand{\Tm}{T_{\rm m}}
\newcommand{\aTm}{\left<\Tm\right>}
\newcommand{\Tmi}{T_{{\rm m},i}}
\newcommand{\Ne}{N_{\rm e}}
\newcommand{\Nm}{N_{\rm m}}
\newcommand{\Nsqmi}{N^2_{{\rm m},i}}
\newcommand{\Nsqm}{N^2_{{\rm m}}}
\newcommand{\rhoTr}{\rho(T,r)}
\newcommand{\Tefit}{T_{e,{\rm fit}}}
\newcommand{\sqravgNi}{\sqrt{\Nsqmi}}
\newcommand{\sqravgN}{\sqrt{\Nsqm}}
\newcommand{\Tc}{T_{\rm c}}
\newcommand{\BibTeX}{\textsc{Bib}\TeX}
\newcommand{\etal}{{\it et al.}}
\newcommand{\Pl}{\texttt{+}}
\newcommand{\Mi}{\texttt{-}}

@@

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/Grispoint_2082_demt_paper_test_Rpoint-map.pdf}
\includegraphics[width=0.495\textwidth,clip=]{figs/Grispoint_2208_demt_paper_test_Rpoint-map.pdf}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_full_Rpoint-map.pdf}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_awsom_paper_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_full_Rpoint-map.pdf}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_full_conajuste_doble_error_Rpoint-map.pdf}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_full_conajuste_doble_error_Rpoint-map.pdf}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_awsom_paper_Rpoint-map.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histo_cr2082_full_conajuste_doble_errorhighpoints.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histo_cr2208_full_conajuste_doble_errorhighpoints.eps}
\caption{\emph{Top panels:} {latitude-longitude location at heliocentric height $r=1.105\,\mrsun$ of all open (grey color) and closed (black color) traced field line legs for which criterion (i) of Section \ref{trace} is met, for both CR-2082 (left) and CR-2208 (right). \emph{Bottom panels}: latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met. {The location of} type 0, I, II and III legs {is shown} in blue, red, {magenta and cyan} color, respectively.}}
\label{rpoint_demt}
\end{center}
\end{figure}

@@

\begin{table}[h!]
\begin{tabular}{l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r  r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r }
\hline
Type    & \multicolumn{4}{c}{$\med(\NCB)$}             & \multicolumn{4}{c}{$\med(\lN)$} & \multicolumn{4}{c}{$\med(\avgTe)$} \\
        & \multicolumn{4}{c}{$[10^8\,{\rm cm}^{-3}]$}  & \multicolumn{4}{c}{$[{\rm 10}^{-2}\,\mrsun]$} & \multicolumn{4}{c}{$[\MK]$} \\
\hline
0    & 1&24 &(\Mi&19\%)  &   7&1 &(\Pl&~3\%) &   1&09 &(\Pl&24\%) \\
I    & 1&15 &(\Mi&10\%)  &   7&5 &(\Pl&29\%) &   1&25 &(\Pl&24\%) \\
II   & 0&98 &(\Mi&20\%)  &   9&9 &(\Pl&19\%) &   1&36 &(\Pl&16\%) \\
III  & 0&66 &(\Mi&\edit{21}\%)  &   7&7 &(\Pl&15\%) &   0&97 &(\Pl&\edit{17}\%) \\
\hline          
\end{tabular}
\caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of legs defined in Section \ref{trace}. For CR-2082 values are expressed in absolute terms, while for CR-2208 they are informed as a percentual variation relative to the CR-2082 value.}
\label{tabla_demt}
\end{table}

@@

\begin{table}
\begin{tabular}{l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r  r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r }
\hline
Type    & \multicolumn{4}{c}{$\med(\NCB)$}             & \multicolumn{4}{c}{$\med(\lN)$} & \multicolumn{4}{c}{$\med(\avgTe)$} \\
        & \multicolumn{4}{c}{$[10^8\,{\rm cm}^{-3}]$}  & \multicolumn{4}{c}{$[{\rm 10}^{-2}\,\mrsun]$} & \multicolumn{4}{c}{$[\MK]$} \\
\hline
CR-2082\\
I    & 1&15 &(\Mi&14\%)  &   7&5 &(\Pl&~8\%) &   1&25 &(\Mi&10\%) \\
II   & 0&99 &(\Mi&25\%)  &   9&9 &(\Mi&~2\%) &   1&36 &(\Mi&~2\%) \\
III  & 0&66 &(\Mi&17\%)  &   7&0 &(\Mi&~9\%) &   0&97 &(\Mi&~9\%) \\
\hline          
CR-2208\\
I    & 1&03 &(\Pl&~6\%)  &   9&7 &(\Mi&~8\%) &   1&55 &(\Mi&17\%) \\
II   & 0&79 &(\Pl&~9\%)  &  11&8 &(\Mi&14\%) &   1&58 &(\Mi&~8\%) \\
III  & 0&\edit{52} &(\edit{\Pl}&~\edit{8}\%)  &   8&9 &(\Mi&18\%) &   1&\edit{13} &(\Mi&18\%) \\
\hline   
\end{tabular}
\caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of leg defined in Section \ref{trace}. DEMT values are expressed in absolute terms, while AWSoM results are expressed relative to the corresponding DEMT value.}
\label{tabla_comp}
\end{table}
